Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
Some details about closures.

\textbf{Having a callback invoked by the adversary}
The above leaves us with probably the hardest scenario: how to provide a
callback to the adversary. The basic idea is that we allocate a block of memory
using malloc that we fill with the capabilities and data that the callback needs
access to, as well as some prelude instructions that load the data into
registers and jumps to the right code. We can then provide the adversary with an
enter-capability covering the allocated block and pointing to the contained
prelude instructions. However, the question that remains in this setup is: where
do we get the stack pointer?

@@

\textbf{Reusable macro instructions} With the high-level approach in mind, we
define the following macro instructions: \texttt{fetch $r$ $\var{name}$} fetches
the capability related to $\var{name}$ from the linking table and stores it in
register $r$. \texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack pointer in register $r_\stk$.
\texttt{prepstk $r$} is used when a callback is invoked by the adversary and
prepares the received stack pointer by checking that it has permission $\rwlx$
and making it conform to our stack discipline. \texttt{scall
  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)} Jumps to the
capability in register $r$ in the manner described above. That is, it pushes local state (the
contents of registers $\overline{r_{\var{priv}}}$), stack pointer and return
pointer to the stack, sets up the necessary on stack return code and creates a
return pointer, restricts stack pointer, clears the unused part of the stack,
clears the necessary registers and jumps to $r$. Upon return, the private state
is restored. \texttt{mclear $r$} clears all the memory the capability in
register $r$ has authority over. \texttt{rclear $\var{regSet}$} clears all the
registers in $\var{regSet}$ \texttt{reqglob $r$} checks whether the word in
register $r$ is a global capability. \texttt{crtcls $\overline{(x_i,r_i)}$ $r$}
allocates a closure pair where the capability in register $r$ is used to point
to the program and a new environment is allocated where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an implicit fetch
happens when an instruction refers to $x_i$.

>>>>

\textbf{Having a callback invoked by the adversary}
The above leaves us with probably the hardest scenario: how to provide a
callback to the adversary. The basic idea is that we allocate a block of memory
using malloc that we fill with the capabilities and data that the callback needs
access to, as well as some prelude instructions that load the data into
registers and jumps to the right code. Note that this implies that no local
capabilities can be stored as part of a closure. We can then provide the adversary with an
enter-capability covering the allocated block and pointing to the contained
prelude instructions. However, the question that remains in this setup is: where
do we get the stack pointer?

@@

\textbf{Reusable macro instructions} With the high-level approach in mind, we
define the following macro instructions: \texttt{fetch $r$ $\var{name}$} fetches
the capability related to $\var{name}$ from the linking table and stores it in
register $r$. \texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack pointer in register $r_\stk$.
\texttt{prepstk $r$} is used when a callback is invoked by the adversary and
prepares the received stack pointer by checking that it has permission $\rwlx$
and making it conform to our stack discipline. \texttt{scall
  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)} Jumps to the
capability in register $r$ in the manner described above. That is, it pushes local state (the
contents of registers $\overline{r_{\var{priv}}}$), stack pointer and return
pointer to the stack, sets up the necessary on stack return code and creates a
return pointer, restricts stack pointer, clears the unused part of the stack,
clears the necessary registers and jumps to $r$. Upon return, the private state
is restored. \texttt{mclear $r$} clears all the memory the capability in
register $r$ has authority over. \texttt{rclear $\var{regSet}$} clears all the
registers in $\var{regSet}$ \texttt{reqglob $r$} checks whether the word in
register $r$ is a global capability. \texttt{crtcls $\overline{(x_i,r_i)}$ $r$}
allocates a closure pair where the capability in register $r$ is used to point
to the program and a new environment is allocated (using malloc) where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an implicit fetch
happens when an instruction refers to $x_i$.
